TODO: A Survey of StarCraft AI Techniques

### 2011-11-24 survey.tex
added the spatial reasoning section

\begin{itemize}
\item Task Decomposition (or ``Architecture'')
\item Integration of Domain Knowledge
\item Reasoning with Uncertainty (including information gathering)
\item Opponent Modeling and Adaptation
\item Group and Individual Control (``micro'')
\item Planning and Resource Allocation (``macro'')
\end{itemize}

@@

@@

For example, notice that a big challenge missing from the above sections is {\em Spatial and Temporal Reasoning}. While I think (and I'm sure you'll agree) that this should be a huge topic in RTS game AI, I haven't seen much of this beyond potential fields. Because of this (as Michael Buro mentioned), many bots fall prey of easy tricks due to lack of common sense reasoning.

>>>>

\begin{itemize}
\item Task Decomposition (or ``Architecture'')
\item Integration of Domain Knowledge
\item Reasoning with Uncertainty (including information gathering)
\item Opponent Modeling and Adaptation
\item Group and Individual Control (``micro'')
\item Planning and Resource Allocation (``macro'')
\item Spatial reasoning
\end{itemize}

@@

\section{Challenge 7: Spatial Reasoning}\label{sec:spatial}

{\color{blue}
I think (and I'm sure you'll agree) that this should be a huge topic in RTS game AI, I haven't seen much of this beyond potential fields. Because of this (as Michael Buro mentioned), many bots fall prey of easy tricks due to lack of common sense reasoning.
}

@@
